MINOS Handover Plots

### 2024-06-26 minos/outcomes/CPR_Intervention_Diagnostics.Rmd

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 
                                    'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)
rel.int <- read_singular_local_out(out.path, 
                                   'ChildPovertyReductionRELATIVE', 
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
# rel.int.2 <- read_singular_local_out(out.path,
#                                      'ChildPovertyReductionRELATIVE_2',
#                                      drop.dead = TRUE,
#                                      drop.zero.weight = TRUE)
# abs.int <- read_singular_local_out(out.path, 
#                                    'ChildPovertyReductionABSOLUTE', 
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
```

>>>>

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 
                                    'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)
# rel.int <- read_singular_local_out(out.path, 
#                                    'ChildPovertyReductionRELATIVE', 
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
rel.int <- read_singular_local_out(out.path,
                                     'ChildPovertyReductionRELATIVE_2',
                                     drop.dead = TRUE,
                                     drop.zero.weight = TRUE)
abs.int <- read_singular_local_out(out.path,
                                   'ChildPovertyReductionABSOLUTE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
```

### 2024-06-26 minos/outcomes/ChildPovReduction_plots.Rmd

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old10/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'treated_relative') { tit <- 'Treated' }
  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

@@

SF12_change_ind_trajectories <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

  p1 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_line(data = plot_data, aes(x = year, y = diff_SF_12, group = run_id), alpha = 0.2) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = 'tit') +
    xlab('Year') +
    ylab('Change in SF-12')

  print(p1)
}

@@

```{r "SF12_change_num_priority_groups", include=FALSE}
SF12_change_num_priority_groups <- function(scen.list) {

  summary_group <- 'priority_num'

  tit <- 'Number of Priority Subgroups'

  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))

  data <- replace_na(data, list(num_priority_groups=0))

  plot_data <- data %>%
    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    select(-scen)

  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)

  plot_data_confint <- plot_data %>%
    group_by(year, num_priority_groups) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  plot_data_confint2 <- plot_data %>%
    group_by(year, num_priority_groups) %>%
    summarise(n = n(),
              mean_SF12_change = mean(diff_SF_12),
              margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Change in SF-12')

SF12_change_percentage_num_priority_groups <- function(scen.list) {

  summary_group <- 'priority_num'

  tit <- 'Number of Priority Subgroups'

  data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))

  data <- replace_na(data, list(num_priority_groups=0))

  plot_data <- data %>%
    select(run_id, num_priority_groups, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ ((. - SF_12.baseline) / SF_12.baseline) * 100)) %>% # Calculate percentage change
    rename_with(~ paste0("percent_change_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("percent_change") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    select(-scen)

  plot_data$num_priority_groups <- factor(plot_data$num_priority_groups)

  plot_data_confint <- plot_data %>%
    group_by(year, num_priority_groups) %>%
    summarise(n = n(),
              mean_SF12_change = mean(percent_change_SF_12),
              margin = qt(0.975, df = n - 1) * (sd(percent_change_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  plot_data_confint2 <- plot_data %>%
    group_by(year, num_priority_groups) %>%
    summarise(n = n(),
              mean_SF12_change = mean(percent_change_SF_12),
              margin = qnorm(0.975) * (sd(percent_change_SF_12) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

  p1 <- ggplot(plot_data, aes(x = year, y = percent_change_SF_12, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted') +
    geom_smooth() +
    labs(title = tit) +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

  p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = num_priority_groups, colour = num_priority_groups, fill = num_priority_groups)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
    labs(title = tit) +
    xlab('Year') +
    ylab('Percentage Change in SF-12')

  print(p1)
  print(p2)
}
```

```{r "inequality_plots", include=FALSE}
inequality_plots <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

  data$income_quintile <- factor(data$income_quintile)

  # Combine the data
  data_combined <- data %>%
    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))

  p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
    geom_smooth(alpha = 0.7) +
    scale_color_manual(name = "Income Quintile", 
                       values = c("red", "blue", "green", "orange", "purple")) +
    scale_linetype_manual(name = "Scenario", 
                          values = c("Baseline" = "solid", "Intervention" = "dotted")) +
    labs(title = "SF_12 Scores by Income Quintile",
         subtitle = tit,
         x = "Year",
         y = "Mean SF_12 MCS") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

  # Aggregate data
  agg_data <- data %>%
    mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
    group_by(year, income_quintile, scenario) %>%
    summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
    spread(scenario, mean_SF_12) %>%
    mutate(difference = Intervention - Baseline)

  p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_manual(name = "Income Quintile", 
                      values = c("red", "blue", "green", "orange", "purple")) +
    labs(title = "Average Difference in SF_12 Scores by Income Quintile",
         subtitle = tit,
         x = "Year",
         y = "Difference in SF_12 Score") +
    theme_minimal() +
    theme(legend.position = "right",
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 10))

  print(p1)
  print(p2)
}
```

```{r "mental_illness_risk", include=FALSE}
mental_illness_risk_counts <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }

  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
  # summary_group <- 'men_illness_risk'

  plot_data <- data %>%
    filter(mental_health_risk == 'TRUE') %>%
    select(-prop, -mental_health_risk) %>%
    pivot_wider(names_from = scen,
                values_from = count) %>%
    rename(intervention = contains(scen.list[[2]])) %>%
    mutate(MHR_diff = intervention - baseline) %>%
    select(run_id, year, MHR_diff) %>%
    group_by(year) %>%
    summarise(MHR_diff = mean(MHR_diff))

  p1 <- ggplot(data = plot_data, aes(x = year, y = MHR_diff)) +
    geom_point() +
    geom_line() +
    labs(title = "Difference in count of individuals at risk of mental health issues",
         subtitle = tit) +
    xlab('Year') +
    ylab('Count')

  plot_data_2 <- data %>%
    filter(mental_health_risk == 'TRUE') %>%
    select(-mental_health_risk, -count) %>%
    pivot_wider(names_from = scen,
                values_from = prop) %>%
    rename(intervention = contains(scen.list[[2]])) %>%
    mutate(MHR_prop_diff = intervention - baseline) %>%
    select(run_id, year, MHR_prop_diff) %>%
    group_by(year) %>%
    summarise(MHR_prop_diff = mean(MHR_prop_diff))

  p2 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_prop_diff)) +
    geom_point() +
    geom_line() +
    labs(title = "Difference in proportion of individuals at risk of mental health issues",
         subtitle = tit) +
    xlab('Year') +
    ylab('Proportion')

  print(p1)
  print(p2)
}
```

```{r}
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
#scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
#scen.list.test <- c('baseline', 'ChildPovertyReductionSUSTAIN')
whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
```

@@

SF12_change_percentage(summary_group = 'whole_pop',
                       scen.list = scen.list.test)

SF12_change_ind_trajectories(summary_group = 'whole_pop',
                             scen.list = scen.list.test)

inequality_plots(summary_group = 'whole_pop',
                 scen.list = scen.list.test)

mental_illness_risk_counts(summary_group = 'men_illness_risk',
                           scen.list = scen.list.test)
```

@@

SF12_change_percentage(summary_group = 'families',
                       scen.list = scen.list.test)

SF12_change_ind_trajectories(summary_group = 'families',
                             scen.list = scen.list.test)

inequality_plots(summary_group = 'families',
                 scen.list = scen.list.test)

mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
                           scen.list = scen.list.test)
```

# Treated

```{r}
SF12_change_simple(summary_group = 'treated_relative',
                   scen.list = scen.list.test)

SF12_change_percentage(summary_group = 'treated_relative',
                       scen.list = scen.list.test)
```

@@

## Number of Priority Subgroups

```{r}
SF12_change_num_priority_groups(scen.list.test)
SF12_change_percentage_num_priority_groups(scen.list.test)
```

# TESTING

@@

# TESTING

```{r}
SF12_change_simple <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'treated_relative') { tit <- 'Treated' }
  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

  print(p1)
  print(p2)
  #print(p3)
}
```

## NEW CONFINTS

summary_group <- 'whole_pop'
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')

data <- do.call(rbind, generate_df_list(summary_group, scen.list.test))

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

@@

@@

@@

```{r}
#scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
```

@@

SF12_change_percentage(summary_group = 'whole_pop',
                       scen.list = scen.list.test)
```

@@

SF12_change_percentage(summary_group = 'families',
                       scen.list = scen.list.test)
```

@@

```{r}
#SF12_change_income_quint <- function(summary_group, scen.list) {

# summary_group <- 'priority_num'
# 
#   tit <- ' '
#   if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
#   if (summary_group == 'families') { tit <- 'Families' }
# 
#   #summary_group <- paste0(summary_group, '_income_quint')
# 
#   data <- do.call(rbind, generate_df_list(summary_group, scen.list))
# 
#   plot_data <- data %>%
#     select(run_id, income_quintile, SF_12, mean_cost, year, scen) %>%
#     pivot_wider(names_from = scen,
#                 values_from = c(SF_12, mean_cost),
#                 names_sep = '.') %>%
#     mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
#     rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
#     pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
#                  names_to = c(".value", "scen"),
#                  names_sep = "\\.") %>%
#     filter(scen != 'baseline') %>%
#     select(-scen)
# 
#   plot_data$income_quintile <- factor(plot_data$income_quintile)
# 
#   plot_data_confint <- plot_data %>%
#     group_by(year, income_quintile) %>%
#     summarise(n = n(),
#               mean_SF12_change = mean(diff_SF_12),
#               margin = qt(0.975, df = n - 1) * (sd(diff_SF_12) / sqrt(n)),
#               lower = mean_SF12_change - margin,
#               upper = mean_SF12_change + margin)
# 
#   plot_data_confint2 <- plot_data %>%
#     group_by(year, income_quintile) %>%
#     summarise(n = n(),
#               mean_SF12_change = mean(diff_SF_12),
#               margin = qnorm(0.975) * (sd(diff_SF_12) / sqrt(n)),
#               lower = mean_SF12_change - margin,
#               upper = mean_SF12_change + margin)
# 
# 
#   p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
#     geom_hline(yintercept = 0, linetype = 'dashed') +
#     geom_vline(xintercept = 2030, linetype = 'dotted') +
#     geom_smooth() +
#     labs(title = tit, subtitle = 'Income Quintile') +
#     xlab('Year') +
#     ylab('Change in SF-12')
# 
#   p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
#     geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
#     geom_line(linetype = 'dashed') +
#     geom_point() +
#     geom_hline(yintercept = 0, linetype = 'dashed') +
#     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
#     labs(title = tit, subtitle = 'Income Quintile') +
#     xlab('Year') +
#     ylab('Change in SF-12')
# 
#   p3 <- ggplot(plot_data_confint2, aes(x = year, y = mean_SF12_change, group = income_quintile, colour = income_quintile, fill = income_quintile)) +
#     geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
#     geom_line(linetype = 'dashed') +
#     geom_point() +
#     geom_hline(yintercept = 0, linetype = 'dashed') +
#     geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
#     labs(title = tit, subtitle = 'Income Quintile') +
#     xlab('Year') +
#     ylab('Change in SF-12')
# 
#   print(p1)
#   print(p2)
#}
```

@@

### 2024-06-26 minos/validation/handovers.Rmd

```{r}
# Read raw datafiles in
#raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

@@

# Need to remove extra data from raw data after start year
raw.dat <- raw.dat %>%
  filter(time <= start.year)

@@

ggplot(combined, aes(x = time, y = age_group_counts, group = age_group, colour = age_group)) +
  geom_line() +
  geom_vline(xintercept = start.year, linetype = 'dashed') +
  labs(title = 'Counts by older age group', subtitle = '75 to 110 by 5 year groups') +
  xlab('Year') +
  ylab('Count')

@@

ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = start.year, linetype = 'dashed') +
  labs(title = 'Households Count')
```

@@

spaghetti_plot(base.inc, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

@@

#### Absolute
```{r}
# raw.2010 <- raw.dat %>%
#   filter(time == 2010)
# 
# abs.threshold <- weighted.median(x = raw.2010$hh_income, 
#                                  w = raw.2010$weight, 
#                                  na.rm = TRUE)
# abs.threshold <- abs.threshold * 0.6
# 
# print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
```

>>>>

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

@@

@@

ggplot(combined, aes(x = time, y = age_group_counts, group = age_group, colour = age_group)) +
  geom_line() +
  geom_vline(xintercept = 2021, linetype = 'dashed') +
  labs(title = 'Counts by older age group', subtitle = '75 to 110 by 5 year groups') +
  xlab('Year') +
  ylab('Count')

@@

ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
  geom_point() +
  geom_line() +
  labs(title = 'Households Count')
```

@@

@@

#### Absolute
```{r}
raw.2010 <- raw.dat %>%
  filter(time == 2010)

abs.threshold <- weighted.median(x = raw.2010$hh_income, 
                                 w = raw.2010$weight, 
                                 na.rm = TRUE)
abs.threshold <- abs.threshold * 0.6

print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
```
